Community-Conditioned Language Models

### 2020-11-11 paper/paper.tex
add pairwise similarity plot/table

\subsection{Analysis of community embeddings}

As a qualitative assesment of the community embeddings, 
we identified several topic categories into which at least three
of the selected communities fall. 
We plotted the two-component PCA projection of the embeddings,
annotated with these topic categories (Figure~\ref{fig:comm-pca}).
We see that there is some evidence of clustering according to
the topic categories we identified,
suggesting that the embedding space learned by the model is meaningful.

@@

As a quantitative ....

- Correlation with community embeddings based on co-occurence;

@@

- Insert scatterplot (select 1 model)
  + pearson r for ``all'' models.

>>>>

\subsection{Analysis of CCLM community embeddings}

As a qualitative assesment of the community embeddings, 
we manually identified topic categories into which at least three
of the selected communities fall. 
We plotted the two-component PCA projection of the embeddings,
annotated with these categories (Figure~\ref{fig:comm-pca}).
We see that there is some evidence of clustering according to
the topic categories we identified,
suggesting that the embedding space learned by the model is meaningful.

@@

As a quantitative assessment,
we compare the CCLM-learned community embedding with the community embedding from \citet{Kumar2018},
which is based on community membership.

@@

We correlate the pairwise cosine similarity of the
CCLM embeddings with the same metric on the membership embedding,
restricted to the 46 communities chosen for our study
(Figure~\ref{fig:pairwise-comm-sim}).

\begin{figure}
  \begin{tikzpicture}
  \begin{axis}[]
  \addplot[
    scatter, only marks,
    font=\tiny,
    scatter src=explicit symbolic,
    scatter/classes={
      general-interest={mark=*, blue},
      videogames={mark=*, red},
      technology={mark=*, green},
      sports={mark=*, cyan},
      female-focused={mark=*, magenta},
      other={mark=o, black},
      different={mark=x}
    },
    %mark size=1pt,
    %nodes near coords*={\community},
    %visualization depends on={value \thisrow{community} \as \community}
  ] table [x=snap, y=lstm-3-1, meta=meta] {floats/comm_sim.csv};
  \end{axis}
  \end{tikzpicture}
  \caption{Pairwise cosine similarity between community vectors for 
    the membership-based embedding (x-axis) and
  the LSTM CCLM embedding with $c=1$ (y-axis). 
  Pairs from the same category are colored according to Figure~\ref{fig:comm-pca}.
  We also mark pairs from different (\texttimes) and pairs where one or both
  communities belong to the ``Other'' category (\textbigcircle).
  }
  \label{fig:pairwise-comm-sim}
\end{figure}

\begin{table}
  \centering
  \input{floats/comm_sim.tex}
  \caption{Pearson's r between the pairwise similarity of community vectors
  in the CCLM models and the membership-based embedding of \citet{Kumar2018}.
  ($p<0.001$ for all models).
  }
  \label{tab:pairwise-comm-sim}
\end{table}

### 2020-11-11 paper/plot_macros.tex
add pairwise similarity plot/table

\newcommand{\commpcagroupplot}[2]{%
  \begin{groupplot}[
    group style={group size=2 by 1}, 
    yticklabels={,,}, xticklabels={,,},
    legend style={anchor=north, legend columns=1, font=\tiny}%
    ]
    \nextgroupplot
    \commpcaplot{#1}
    \nextgroupplot
    \commpcaplot{#2}
    \legend{General interest,Videogames,Technology,Sports,Female-focused,Other}
  \end{groupplot}
}

>>>>

\newcommand{\commpcagroupplot}[2]{%
  \begin{groupplot}[
    group style={group size=2 by 1}, 
    yticklabels={,,}, xticklabels={,,},
    legend style={anchor=north, legend columns=1, font=\tiny},
    every node near coord/.append style={font=\sffamily\tiny}%
    ]
    \nextgroupplot
    \commpcaplot{#1}
    \nextgroupplot
    \commpcaplot{#2}
    \legend{General interest,Videogames,Technology,Sports,Female-focused,Other}
  \end{groupplot}
}

\newcommand{\confusionplot}[1]{%
    \addplot[
        matrix plot*,
        shader=faceted,
        mesh/cols=46,
        point meta=explicit,
] table [x=actual_comm, y=confered_to, meta=avg_prob] {#1};
}

\newcommand{\confusiongroupplot}[2]{%
  \begin{groupplot}[
  group style={group size=2 by 1}, 
  enlargelimits=false,
  axis line style={draw=none},
  %axis equal,
  xmin=-1, xmax=46,
  ymin=-1, ymax=46,
  width=8cm,
  xticklabels={Advice,AskWomen,BabyBumps,CFB,Drugs,EDH,EarthPorn,Fantasy,GameDeals,GlobalOffensive,Jokes,Kappa,KerbalSpaceProgram,KotakuInAction,LifeProTips,MLS,MMA,MaddenUltimateTeam,TwoXChromosomes,Warframe,airsoft,bodybuilding,breakingmom,cars,cringe,eu4,exjw,explainlikeimfive,femalefashionadvice,food,heroesofthestorm,jailbreak,justneckbeardthings,oculus,pcmasterrace,photography,reddevils,relationships,rupaulsdragrace,stopdrinking,streetwear,techsupport,todayilearned,toronto,videos,xxfitness},
  yticklabels=none,
  xticklabel style={font=\sffamily\tiny, rotate=90},
  xtick=data,
  legend style={font=\sffamily\small},
    ]
    \nextgroupplot
    \confusionplot{#1}
    \nextgroupplot[colorbar right]
    \confusionplot{#2}
  \end{groupplot}
}
